---
title: "infuser"
output: md_document
---

[![Travis-CI Build Status](https://travis-ci.org/zachmayer/infuser.svg?branch=master)](https://travis-ci.org/zachmayer/infuser)
[![Coverage Status](https://img.shields.io/coveralls/zachmayer/infuser.svg)](https://coveralls.io/r/zachmayer/infuser?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/infuser)](http://cran.r-project.org/web/packages/infuser)
[![Downloads](http://cranlogs.r-pkg.org/badges/infuser)](http://cran.rstudio.com/package=infuser)

```infuser``` is a simple and very basic templating engine for R. It replaces parameters within templates with specified values. Templates can be either contained in a string or in a file.

### Installation

```{r, eval=FALSE}
install.packages("infuser")
```

### Usage

Let's have a look at an example string.

```{r}
my_sql<-"SELECT * FROM Customers
WHERE Year = {{year}}
AND Month = {{month|3}};"
```

Here the variable parameters are enclosed by ```{{``` and ```}}``` characters. See ```?infuse``` to use your own specification.

From now on, we suppose the character string ```my_sql```  is our template. To show the parameters requested by the template you can run the following.

```{r, results='hide'}
library(infuser)
variables_requested(my_sql, verbose = TRUE)
```

To fill in the template simply provide the requested parameters.

```{r}
infused_sql<-
infuse(my_sql, year=2016, month=8)

cat(infused_sql)
```

If a default value is available in the template, it will be used if the parameter is not specified.

```{r}
infused_sql<-
infuse(my_sql, year=2016)

cat(infused_sql)
```

Just like we're using a string here, a text file can be used. An example text file can be found in the package as follows:

```{r}
example_file<-
  system.file("extdata", "sql1.sql", package="infuser")

example_file
```

Again, we can check which parameters are requested by the template.

```{r, results='hide'}
variables_requested(example_file, verbose = TRUE)
```

And provide their values.

```{r}
infused_template<-
  infuse(example_file, year = 2016, month = 12)

cat(infused_template)
```

### Issues / questions

Simply create a new issue at this GitHub repository.
