---
title: "infuser"
output: md_document
---

[![Travis Build Status](https://travis-ci.org/Bart6114/infuser.svg)](https://travis-ci.org/Bart6114/infuser)
[![Coverage Status](https://coveralls.io/repos/Bart6114/infuser/badge.svg)](https://coveralls.io/r/Bart6114/infuser)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/infuser)](http://cran.r-project.org/web/packages/infuser)
[![Downloads](http://cranlogs.r-pkg.org/badges/infuser)](http://cran.rstudio.com/package=infuser)

```infuser``` is a simple and very basic templating engine for R. It replaces parameters within templates with specified values. Templates can be either contained in a string or in a file.

## Installation

```{r, eval=FALSE}
install.packages("infuser")
```

## Usage

### Working with character strings as templates

Let's have a look at an example string.

```{r}
my_sql<-"SELECT * FROM Customers
WHERE Year = {{year}}
AND Month = {{month|3}};"
```

Here the variable parameters are enclosed by ```{{``` and ```}}``` characters. See ```?infuse``` to use your own specification.

From now on, we suppose the character string ```my_sql```  is our template. To show the parameters requested by the template you can run the following.

```{r, results='hide'}
library(infuser)
variables_requested(my_sql, verbose = TRUE)
```

To fill in the template simply provide the requested parameters.

```{r}
infused_sql<-
infuse(my_sql, year=2016, month=8)

cat(infused_sql)
```

If a default value is available in the template, it will be used if the parameter is not specified.

```{r}
infused_sql<-
infuse(my_sql, year=2016)

cat(infused_sql)
```

### Working with text files as templates

Just like we're using a string here, a text file can be used. An example text file can be found in the package as follows:

```{r}
example_file<-
  system.file("extdata", "sql1.sql", package="infuser")

example_file
```

Again, we can check which parameters are requested by the template.

```{r, results='hide'}
variables_requested(example_file, verbose = TRUE)
```

And provide their values.

```{r}
infused_template<-
  infuse(example_file, year = 2016, month = 12)

cat(infused_template)
```

### Processing / tranforming your inputs

A ```transform_function``` can be specified in the ```infuse``` command. This allows for pre-processing of the parameter values before inserting them in the template.

What we don't want to happen is the following:

```{r}
sql<-"INSERT INTO Students (Name) VALUES ({{name}})"
name <- "'Robert'); DROP TABLE Students;--"

cat(
  infuse(sql, name = name)
)
```

Yikes! A way to solve this is to specify a custom transform function:

```{r}
cat(
  infuse(sql, name = name, transform_function = dplyr::build_sql)
)
```

## Issues / questions

Simply create a new issue at this GitHub repository.
